I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-17 Paper/Paper_noProof.tex
update paper

First, remark that weighted sums is a linear function, so it is easy to represent it explicitly. The only problematic part to represent accurately is the ReLU function. While it is fairly simple piecewise linear function with 2 modes ($x<0$ and $x \geq 0$), it is not linear. Considering its iterated impact along the different layers of a ReLU DNN is much more complex that it seems. First, let us remark that it is easy to represent exactly $ReLU(x)$
in case $x$ is known to be entirely positive and in the case where it is entirely negative
(such a neuron $x$ is called stable), as in both case there is only one known linear mode involved. Hence, the sole problem remains how to treat unstable neurons.

>>>>

First, remark that weighted sums is a linear function, so it is easy to represent it explicitly. The only problematic part to represent accurately is the ReLU function. While it is fairly simple piecewise linear function with 2 modes ($x<0$ and $x \geq 0$), it is not linear. Considering its iterated impact along the different layers of a ReLU DNN is much more complex that it seems. First, let us remark that it is easy to represent exactly $\ReLU(x)$
in case $x$ is known to be entirely positive and in the case where it is entirely negative
(such a neuron $x$ is called stable), as in both case there is only one known linear mode involved. Hence, the sole problem remains how to treat unstable neurons.
